On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-19 MS.tex
editing MS

We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth rate (Table \ref{tab:trade-offs}). We supplemented records from our own bibliographic libraries with results from searching online databases and suggestions from other researchers. Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters). While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e. title, keywords, and abstracts, \citealt{Beckmann:2012hn}). This limitation does not apply to Google Scholar.

The biggest challenge when searching literature databases is to identify suitable studies from the vast corpus available. Initially we were interested to know whether data existed for a variety of traits; however the number of potential search terms made systemic searching for all these terms in Google Scholar impractical. A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and WD -- two of the most widely measured traits -- would capture  $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot}). We therefore narrowed our searching to only cover these two main traits.

Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate. On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''). This keyword search in Google Scholar returned approximately 18900 papers. We examined all records returned from the Web of Science search (XXX) and the first 750 items from Google Scholar when ranked by ``relevance''. All searches were conducted between March and December 2014.

@@

We recorded coefficient correlations for a list of 19 traits (Fig. \ref{fig:fig1}): the five for which we had prior expectations, plus 14 others commonly used in the trait literature. SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.

Ultimately, data was recorded from from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

The entire dataset included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth rate. The main results reported here were obtained with an ``ideal'' subset of data. This ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait). These were then compare against results obtained with the entire dataset, including all noted correlations.

@@

TODO: XXXX

We first developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.

>>>>

We aimed to identify studies reporting a correlation across species, between functional traits and growth rate (e.g. relative or absolute growth, in diameter, height or mass, see Table \ref{tab:trade-offs}. Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters). While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e. title, keywords, and abstracts, \citealt{Beckmann:2012hn}). This limitation does not apply to Google Scholar. We supplemented these records with results from our own bibliographic libraries and suggestions from other researchers.

A big challenge when searching literature databases is to identify suitable studies from the vast corpus available. Initially we were interested to know whether data existed for a variety of traits; however the number of potential search terms made systemic searching for all these terms in Google Scholar impractical. A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and WD -- two of the most widely measured traits -- would capture $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot}). We therefore narrowed our searching to only cover these two main traits.

Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate. On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ). On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''). This keyword search in Google Scholar returned approximately 18900 papers. We examined all records returned from the Web of Science search (XXX) and the first 750 items from Google Scholar when ranked by ``relevance''. All searches were conducted between March and December 2014.

@@

The 19 traits recorded (Fig. \ref{fig:fig1}) capture different components of plant ecological strategies. SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.

Ultimately, data was recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

The entire dataset included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth rate. The main results reported here were obtained with an ``ideal'' subset of data. This ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait). These were then compare against results obtained with the entire dataset (including all noted correlations).

@@

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.
